---
title: "DATA 606 Presentations"
subtitle: "Statistics & Probability for Data Analytics"
date: "Fall 2024"
output:
  xaringan::moon_reader:
    css: ["assets/mtheme_max.css", "assets/fonts_mtheme_max.css"]
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: solarized-light
      highlightLanguage: R
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
    includes:
      in_header: [assets/header.html]
      after_body: [assets/insert-logo.html]
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
source('../config.R')
```

class: center, middle, inverse, title-slide

# `r metadata$title`
## `r metadata$subtitle`
### `r metadata$author`
### `r metadata$date`


---
class: font90
# Rubric

```{r, echo = FALSE}
rubric <- readxl::read_excel('../Project/Data_Project_Rubric.xlsx')
kable(rubric)
```

---
class: font100
# Directions

* You have no more than 10 minutes.

* If your abstract is in your slide deck, please don't read it.

* We will record the session for our records but will not post the recording.

* Complete the peer feedback form for each presentations: https://forms.gle/5twhtAUwdBgzdJA19

* You will receive your feedback from us and peers (anonymized) after all the presentations have been done.

* Submit a PDF of your slides and abstract to Brightspace.

* Good luck!
